\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Duy}{Dinh}


\phone[mobile]{(512)893-9661}               
\email{defduydinh@gmail.com}                             


\begin{document}

\newcommand{\employer}{University of Texas System}
\newcommand{\position}{Information Technology}
\newcommand{\schyear}{Junior}
\newcommand{\found}{Handshake}

\recipient{To}{ Employer of \employer \\
                \position \ Internship}

\date{\today}
\opening{Greeting!}
\closing{Thank you for your time and consideration!}
\enclosure[Attachment]{CV}

\makelettertitle

I am writing to express my interest in \position internship at your office. I notice this intern opportunity through your internship listing on \found.

\bigskip

I am currently a \schyear \ at University of Texas at Dallas, majoring in Computer Science with focuses in Cybersecurity and Information Technology courses.



\bigskip

Previously, I worked as a customer service associate at a local electronic store, working on improving customer’s shopping experience while maintaining a safe work environment. During my experience there, I developed an essential communication skill to interact with customers and supervisors, while also demonstrated my ability to resolve a variety of issues and complaint with professional manner. I believe that my skill from working as customer service will elevate team-communication at your office, as it is important to provide concise and accurate report to increase security of information.

\bigskip

I would like an opportunity to meet with you to discuss my internship application for your office. Please contact me via email of \email or through mobile phone \phone.

\vspace{0.5cm}


\makeletterclosing

\end{document}
