\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Duy}{Dinh}


\phone[mobile]{(512)893-9661}               
\email{defduydinh@gmail.com}                             


\begin{document}

\newcommand{\employer}{University of Texas System}
\newcommand{\position}{Cybersecurity }
\newcommand{\schyear}{junior }

\recipient{To}{ Employer of \employer \\
                \position Internship}

\date{\today}
\opening{Greeting!}
\closing{Thank you for your time and consideration!}
\enclosure[Attachment]{CV}

\makelettertitle

I am writing to express my interest in an internship position for \position at your office. I notice this intern opportunity through your intern listing on Handshake. \\

\bigskip

I am a \schyear at University of 
I am proficient at writing scripts to create tools to assist and/or solve with problems. Through my experience of fiddling with consumer network devices, I have developed a good understanding of the network system. I feel that your company will further enhance my skill and knowledge of network security and vulnerability through this internship opportunity, while also creating new view of security management at your company. Through your internship opportunity, I will learn how to handle security system, identify potential vulnerability, and learn to handle situations with professional manner. I hope to introduce skills I learned from my previous job and develops usable tools to your office.

\bigskip

Previously, I worked as a customer service associate at a local electronic store, working on improving customer’s shopping experience while maintaining a safe work environment. During my experience there, I developed an essential communication skill to interact with customers and supervisors, while also demonstrated my ability to resolve a variety of issues and complaint with professional manner. I believe that my skill from working as customer service will elevate team-communication at your office, as it is important to provide concise and accurate report to increase security of information.

\bigskip

I would like an opportunity to meet with you to discuss my internship application for your office. Please contact me via email of \email or through mobile phone \phone.

\vspace{0.5cm}


\makeletterclosing

\end{document}
