\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}
\usepackage{blindtext}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Duy}{Dinh}


\phone[mobile]{(512)893-9661}               
\email{defduydinh@gmail.com}                             


\begin{document}

\newcommand{\employer}{University of Texas System}
\newcommand{\position}{Information Technology}
\newcommand{\schyear}{Junior}
\newcommand{\found}{Handshake}

\recipient{To}{ Employer of \employer \\
                \position \ Internship}

\date{\today}
\opening{Greeting!}
\closing{Thank you for your time and consideration!}
\enclosure[Attachment]{CV}

\makelettertitle

I am writing to express my interest in \position internship at your office. I notice this intern opportunity through your internship listing on \found.

\bigskip

I am currently a \schyear \ at the University of Texas at Dallas, majoring in Computer Science with focuses on Cybersecurity and Information Technology courses.
I had prior IT experiences at home through my experiences and knowledge about computer hardware and networking devices. As a first-generation student in college and an immigrant, I am the only one in my family who is familiar with technology and is responsible for any IT task at home.

\bigskip

Personal IT experiences:
\begin{itemize}
    \item Manage and host game servers. Performed necessary server version upgrades.
    \item Remote access into other computers to diagnose and attempt to fix problems.
    \item Upgrade home network and made necessary configuration for reliability.
    \item Build computers using off-shelf hardware components. Replace unusable or old components.
    \item Proficient in using Microsoft Office's applications.
\end{itemize}


\bigskip

Previously, I worked as a customer service associate at a local electronic store. During my employment, I developed an essential communication skill to interact with customers and supervisors, while also demonstrated my ability to resolve a variety of issues and complaints in a professional manner. I also expanded my knowledge about the IT field through my coworker.

\bigskip

I believe that my tech-savvy characteristic, dedication, and knowledge in \position would prove to be beneficial at your office.

\bigskip
I like an opportunity to meet with you to discuss my internship application for your office. Please contact me via email of \email or through mobile phone \phone.

\vspace{0.5cm}


\makeletterclosing

\end{document}
